Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2014-06-10 Referee2_Response.tex

\begin{itemize}
\item[] \textit{6, 30: Explicitly say what the d.f.\ in (2) is.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{7, 46: Does $\gamma$ need to be an integer? 
You seem to be using it that way, so maybe state the requirement.}
\end{itemize}

\noi
Yes; we now explicitly state this in a sentence after we introduce $\gamma$. 
\medskip

@@

\begin{itemize}
\item[] \textit{8, 4 (and elsewhere): Define notations such as floor and ceiling functions.}
\end{itemize}

\noi
Done. 
We introduced the floor function before its first use and similarly, we introduced the ceiling function before its first use. 
\medskip

@@

\begin{itemize}
\item[] \textit{8, 53--57: The various OBM references should have been discussed earlier.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{10, 11 (and elsewhere): ``$E[f(x, \xi)^4]$'' instead of ``$Ef(x, \xi)^4$'' (never hurts to use some brackets to reduce ambiguity)}
\end{itemize}

\noi
Changed.
In fact, we now use brackets for all the expectations in the paper to improve clarity.
Thank you for this suggestion. 
\medskip

@@

\begin{itemize}
\item[] \textit{11, 33: It might be helpful to add a step before the first inequality in the proof.}
\end{itemize}

\noi
Instead of adding another step before the first inequality in the proof of Lemma 1, we added explanations at the beginning of the proof to make this inequality clear.   
\medskip

\begin{itemize}
\item[] \textit{12, 52: ``$n_l VD_l$ has been studied''}
\end{itemize}

@@

\begin{itemize}
\item[] \textit{13, 12 (and elsewhere): I may have missed this, but has the notation $\sigma_{\hat{x}}$ been established yet? 
In any case, some of the verbiage in this paragraph is a bit repetitive.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{13, 44: Is the expression for d.f. too big?}
\end{itemize}

\noi
We now denote it as `dt' to represent the whole denominator term (d.t.). 
\medskip

@@

\begin{itemize}
\item[] \textit{13, 53: The reader might need another step besides C-S to get that inequality.}
\end{itemize}

\noi
This is a direct application of the Cauchy-Schwartz inequality $\left(\sum_{j=1}^{n}x_j y_j\right)^2 \leq \sum_{j=1}^{n}x_j^2 \sum_{j=1}^{n}y_j^2$, where the $y_j$ are all set to $1$. 
We added a brief explanation after this inequality to make it clear. 
\medskip

@@

\begin{itemize}
\item[] \textit{15, 25: Do you discuss $t_{d_l,\alpha}$ at all in Theorem 3?}
\end{itemize}

\noi
No, we did not.   
We added explanations in the proof Theorem 3, discussing how $t_{d_l,\alpha}$ factors in the proof. 
\medskip

### 2014-06-10 omrp_lb_rev.tex
More Referee 2 suggestions

% Commands for probability
\newcommand{\p}[1]{\mathbb{P} \left\{ #1 \right\}}
\newcommand{\e}[1]{\mathbb{E} %\left[ 
#1 %\right]
}
\newcommand{\ee}[2]{\mathbb{E}_{#1} \left[ #2 \right]}
\newcommand{\var}[1]{\mathrm{Var} \left( #1 \right)}
\newcommand{\cov}[1]{\mathrm{Cov} \left( #1 \right)}
\newcommand{\cor}[1]{\mathrm{Corr} \left( #1 \right)}
\newcommand{\varh}[1]{\widehat{\mathrm{Var}} \left( #1 \right)}
\newcommand{\vart}[1]{\widetilde{\mathrm{Var}} \left( #1 \right)}
\newcommand{\vartg}[1]{\widetilde{\mathrm{Var}}_\gamma \left( #1 \right)}
\newcommand{\varhat}{\widehat{\mathrm{Var}}}

@@

As before, let $m$ denote the batch size, $n$ the total sample size and $k = \lfloor \tfrac{n}{m} \rfloor$ be the number of nonoverlapping batches.  
In this paper, we use the {\it batch nonoverlap parameter} $1 \leq \gamma \leq m$ to denote how much neighboring batches do {\it not} overlap.  
For instance, $\gamma = m$ corresponds to the classical case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally overlapping case of \citet{Meketon1984}.  
The sample mean of each batch estimator is calculated similarly, 
$
\yb_j = \frac{1}{m} \sum_{i=1}^m y^{\gamma(j-1) + i},\ \  j = 1, 2, \dots, \nb, 
$
where $\nb$ is the number of batches used given $n$, $m$ and $\gamma$.  
The sample variance estimator given in (\ref{eq:overlap_variance_def}) is changed to
\begin{equation} \label{eq:variance_gamma}
	\vartg{\ybb} = \frac{1}{\left( \tfrac{n}{m} - 1 \right) \left( \nb \right)}  \sum_{j=1}^{\nb} (\yb_j - \ybb)^2.
\end{equation}
Note that with $\gamma=1$, (\ref{eq:variance_gamma}) reduces to (\ref{eq:overlap_variance_def}) and with $\gamma=m$ and $n=mk$, (\ref{eq:variance_gamma}) reduces to (\ref{eq:var}).

The amount of asymptotic variance reduction in this estimator depends on the asymptotic ratio of $\gamma/m$, which we denote by $\gammab$.  
For example, when $\gamma = 1$ (or $\gammab=0$; the maximally overlapping case), the variance is reduced to two-thirds ($66.67\%$) of the original nonoverlapping case, as given in (\ref{eq:asym_var}).  
When 75\% of observations overlap (i.e., when $\gamma = m/4$ or $\gammab = 1/4$), the variance is $33/48$th of the original ($68.75\%$), which is near-optimal.   
When only half of the observations overlap ($\gammab = 1/2$) the variance is 75\% of original.  
In general, from the spectral analysis given in \citep{Welch1987}, the variance is reduced to
\begin{equation} \label{eq:var_reduct_formula}
	\gammab \left( 1 + 2 \sum_{j=1}^{\cogb-1} (1-j\gammab)^2 \right) %= -\gammab\left( 1 - 2\gammab\cogb + \gammab^2\cogb^2 \right) + 2\gammab\cogb\left(1-\gammab\cogb\right) + \frac{2}{3}\gammab^3\cogb^3 + \frac{1}{3}\gammab^3\cogb
\end{equation}
of the nonoverlapping case.  
If $\ogb$ is an integer, (\ref{eq:var_reduct_formula}) simplifies to $\frac{2+\gammab^2}{3}$.

@@

\begin{proof} Let $E^C$ denote the complement of event $E$. Note that
	\begin{align}
		\p{\dbb_l - \gbb_l \neq 0} & \leq \p{\left( \bigcap_{j=1}^{\nbl} \{\xs_{j} = \xs\} \right)^C} \notag \\
		& = \p{ \bigcup_{j=1}^{\nbl} \{\xs_{j} \neq \xs\}} \notag \\
% 		& \leq \sum_{j=1}^{\nbl} \p{ \xs_j \neq \xs } \notag \\
		& \leq \left( \nbl\right) \p{ \xs_{m_l} \neq \xs }. \notag
	\end{align}
	With a batching structure in which $m_l = \lfloor n_l^{r} \rfloor$ for some $0<r<1$,  $\gamma_l \geq 1$, and by A3, the desired result follows.
\end{proof}

@@

Part (i) of Theorem \ref{thm:strong_consistency} provides conditions under which the point estimator $\gbb$ of OMRP is a consistent estimator of the optimality gap, by establishing almost sure convergence of $\gbb_l - \dbb_l$ to $0$ as $l \rightarrow \infty$. 
Notice that under assumption A1, $\dbb_l \rightarrow \mu_\xh$, a.s. by the strong law of large numbers; as a result, $\gbb \rightarrow \mu_\xh$, a.s. 
Similarly, part (ii) of Theorem \ref{thm:strong_consistency} establishes almost sure convergence of $n_l VG_l - n_l VD_l$ to $0$ as $l \rightarrow \infty$. 
As a result, if $n_l VD_l$ is a consistent estimator of $\sigma^2_{\xh}$, so is $n_l VG_l$.  
Strong consistency of the variance estimator $n_l VD_l$ have been studied in \citep{damerdji1994strong} for the cases of nonoverlapping and maximally overlapping batches.  
Under the additional moment assumption
\begin{description}
	\item[A2$^\prime$]  $\exists \epsilon > 0$ such that $\sup_{\x \in X} \e{f(\x,\xi)^{4+\epsilon}} < \infty$,
\end{description}
for a sampling scheme of $m_l = \lfloor n_l^r \rfloor$, Corollaries 3.4 and 4.2 of \citep{damerdji1994strong} show that $n_l VD_l$ is consistent if $\tfrac{2}{4+\epsilon} < r < 1$ for nonoverlapping batches and $\tfrac{2}{4+\epsilon} < r < \tfrac{1}{2}$ for maximally overlapping batches.

@@

\begin{proof}
	For simplicity of exposition, we drop the subscript $l$ and the $\frac{n_l}{m_l}$ for now and add them in later.  
        Further, we use abbreviations $n_b = \nbl$ to denote the number of batches and $df = \left(\tfrac{n_l}{m_l} - 1\right) \left(\nbl\right)$ to denote the denominator term in $VG_l$ and $VD_l$. Note that
	\begin{align}
		\e{(nVG - nVD)^2} & = \left( \frac{n}{df} \right)^2 \e{ \left( \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right] \right)^2 } \notag \\
		& \leq \left( \frac{n}{df} \right)^2 \e{ n_b \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \label{eq:vvar_conv_pf_1}
	\end{align}
	by the Cauchy-Schwartz inequality.  
        By examining the batch structure in Figure \ref{fig:overlap_nonint} and the definition of $\gbb$ in (\ref{eq:gbb}) one can see that the terms of the expectation are not identically distributed.  
        We will separate these into identically distributed ``center'' batches and ``fringe'' batches.  
        For example, in Figure \ref{fig:overlap_nonint}, only batch 4 is a center batch, while the others are fringe batches.  
        Notice in Figure \ref{fig:overlap_nonint}, we see $\left\lceil \gammab^{-1} \right\rceil = 3$ sets of nonoverlapping batches $\{1,4,7\}$, $\{2,5\}$, and $\{3,6\}$, each of which has two fringe batches.  
        In general, there are $\left\lceil \gammab^{-1} \right\rceil$ sets of nonoverlapping batches, each of which will have two fringe batches, and $n_b - 2\left\lceil \gammab^{-1} \right\rceil$ center batches.

	The fringe batches will come in identically distributed pairs.  
        The first and last batch would be identically distributed, as would the second and second-to-last, etc.  
        We know this because we could reverse the order of the i.i.d.\ sample and perform the batching again to get the exact same batch structure.  
        Rewriting to take this into account, letting $A_j = (\gb_j - \gbb)^2 - (\db_j - \dbb)^2$, and continuing from (\ref{eq:vvar_conv_pf_1}),
	\begin{align*}
		& \left( \frac{n}{df} \right)^2 n_b \e{ \sum_{1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \\
		 =  & \left( \frac{n}{df} \right)^2 n_b \e{\left[ \sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
		 + \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
		 + \sum_{j=n_b-\left\lceil \gammab^{-1} \right\rceil+1}^{n_b} \left[ A_j \right]^2 \right]\
		} \\
		 = & \left( \frac{n}{df} \right)^2 n_b \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } + \left( \frac{n}{df} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } \\
		 = & \left( \frac{n}{df} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left[ A_j \right]^2 }
		+ \left( \frac{n}{df} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 }.
	\end{align*}	
	We have $\left\lceil \gammab^{-1} \right\rceil + 1$ expectation terms, each of which has a coefficient that is less than $\left(\frac{n}{df}\right)^2n_b^2 < (2m)^2$.  
        So each expectation can be bounded by
	\begin{align}
		\left( 2m \right)^2 \e{ \left[ A_j \right]^2 } & = \left( 2m \right)^2 \e{ \left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^2 \left[(\gb_j - \gbb) + (\db_j - \dbb)\right]^2 } \notag \\
		& \leq \left( 2m \right)^2 \sqrt{\e{\left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^4}} \sqrt{\e{\left[(\gb_j - \gbb) + (\db_j - \dbb)\right]^4 }} \label{eq:var_reduct_cauchy2} \\
		& \leq \left( 2m \right)^2 \sqrt{\e{\left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^4}} \sqrt{8 \left(\e{(\gb_j - \gbb)^4} + \e{(\db_j - \dbb)^4} \right)}, \label{eq:var_reduct_holder2}
	\end{align}
	where equation (\ref{eq:var_reduct_cauchy2}) follows from the Cauchy-Schwartz inequality, and equation (\ref{eq:var_reduct_holder2}) follows from H\"{o}lder's inequality.  
        Since we can bound both expectation terms in (\ref{eq:var_reduct_holder2}) by A2, we can demonstrate $\sqrt{\frac{n}{m}}(nVG - nVD) \xrightarrow{L^2} 0$ by focusing on only one of the terms.  
        Focusing on the first expectation term in (\ref{eq:var_reduct_holder2}) and returning the $\tfrac{n}{m}$, by H\"{o}lder's inequality,
	\begin{align*}
		\frac{n}{m} 4m^2 \e{\left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^4}	& \leq 32 \frac{n}{m} m^2\left( \e{(\db_j - \gb_j)^4} + \e{(\dbb - \gbb)^4} \right).
	\end{align*}	
	By Lemma \ref{lem:gb_gbb_l4}, both expectation terms above converge to zero with exponential rates.  
        With a batching structure $m_l = \lfloor n_l^r \rfloor$ for some $0<r<1$, we see that $\frac{n_l}{m_l} \e{(n_l VG_l - n_l VD_l)^2} \rightarrow 0$.
\end{proof}

@@

\begin{proof} 
%        With $\xh \neq \xs$, 
			Let $X_l = \frac{\dbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, $Y_l = \frac{\gbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, and $Z_l = \frac{\sigma^2_\xh}{\sqrt{n_lVD_l}} \frac{\sqrt{n_lVD_l}}{\sqrt{n_lVG_l}}$.  
        It is suffices to show $Y_lZ_l = \frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, where $\Rightarrow$ denotes convergence in distribution.  
        First, we show that $|X_l - Y_l| \rightarrow 0$, a.s.  Note that $|X_l - Y_l| > 0$ if and only if $|\dbb_l - \gbb_l| > 0$.  
        In the proof of Theorem \ref{thm:strong_consistency} we showed that $\left\{ \dbb_l - \gbb_l \neq 0 \right\}$ happens only finitely many times, so $|X_l - Y_l| \rightarrow 0$, a.s.\ by the Borel-Cantelli Lemma. 
        Next, since $X_l \Rightarrow N(0,1)$  by the central limit theorem and $|X_l - Y_l| \rightarrow 0$ in probability, $Y_l \Rightarrow N(0,1)$.  
        By hypothesis and Theorem \ref{thm:strong_consistency}, $Z_l \rightarrow 1$ in probability.  
        Thus, by Slutsky's theorem, $Y_lZ_l \Rightarrow N(0,1)$.
\end{proof}

The asymptotic validity of the OMRP CI requires $n_l VD_l$ to converge in probability to $\sigma^{2}_{\xh}$. 
This can be achieved either by almost sure or mean-square convergence, which gives a larger range of $r$ in the batching structure.
Also, a hypothesis of Theorem~\ref{thm:conf_int} is that $\xh \neq \xs$.  For $\xh = \xs$, we have $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1$.

>>>>

% Commands for probability
\newcommand{\p}[1]{\mathbb{P} \left\{ #1 \right\}}
\newcommand{\e}[1]{\mathbb{E} \left[ #1 \right]
}
\newcommand{\ee}[2]{\mathbb{E}_{#1} \left[ #2 \right]}
\newcommand{\var}[1]{\mathrm{Var} \left( #1 \right)}
\newcommand{\cov}[1]{\mathrm{Cov} \left( #1 \right)}
\newcommand{\cor}[1]{\mathrm{Corr} \left( #1 \right)}
\newcommand{\varh}[1]{\widehat{\mathrm{Var}} \left( #1 \right)}
\newcommand{\vart}[1]{\widetilde{\mathrm{Var}} \left( #1 \right)}
\newcommand{\vartg}[1]{\widetilde{\mathrm{Var}}_\gamma \left( #1 \right)}
\newcommand{\varhat}{\widehat{\mathrm{Var}}}

@@

As before, let $m$ denote the batch size, $n$ the total sample size and $k = \lfloor \tfrac{n}{m} \rfloor$ be the number of nonoverlapping batches.  
In this paper, we use the {\it batch nonoverlap parameter} $1 \leq \gamma \leq m$ to denote how much neighboring batches do {\it not} overlap.  
For instance, $\gamma = m$ corresponds to the classical case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally overlapping case of \citet{Meketon1984}.  
In general, $\gamma$ can take any integer value between and including $[1,m]$. 
Let $\lfloor \cdot \rfloor$ be the greatest integer that is less than or equal to its argument. 
The sample mean of each batch estimator is calculated similarly, 
$
\yb_j = \frac{1}{m} \sum_{i=1}^m y^{\gamma(j-1) + i},\ \  j = 1, 2, \dots, \nb, 
$
where $\nb$ is the number of batches used given $n$, $m$ and $\gamma$.  
The sample variance estimator given in (\ref{eq:overlap_variance_def}) is changed to
\begin{equation} \label{eq:variance_gamma}
	\vartg{\ybb} = \frac{1}{\left( \tfrac{n}{m} - 1 \right) \left( \nb \right)}  \sum_{j=1}^{\nb} (\yb_j - \ybb)^2.
\end{equation}
Note that with $\gamma=1$, (\ref{eq:variance_gamma}) reduces to (\ref{eq:overlap_variance_def}) and with $\gamma=m$ and $n=mk$, (\ref{eq:variance_gamma}) reduces to (\ref{eq:var}).

The amount of asymptotic variance reduction in this estimator depends on the asymptotic ratio of $\gamma/m$, which we denote by $\gammab$.  
For example, when $\gamma = 1$ (or $\gammab=0$; the maximally overlapping case), the variance is reduced to two-thirds ($66.67\%$) of the original nonoverlapping case, as given in (\ref{eq:asym_var}).  
When 75\% of observations overlap (i.e., when $\gamma = m/4$ or $\gammab = 1/4$), the variance is $33/48$th of the original ($68.75\%$), which is near-optimal.   
When only half of the observations overlap ($\gammab = 1/2$) the variance is 75\% of original.  
Let $\lceil \cdot \rceil$ be the smallest integer that is greater than or equal to its argument. 
In general, from the spectral analysis given in \citep{Welch1987}, the variance is reduced to
\begin{equation} \label{eq:var_reduct_formula}
	\gammab \left( 1 + 2 \sum_{j=1}^{\cogb-1} (1-j\gammab)^2 \right) %= -\gammab\left( 1 - 2\gammab\cogb + \gammab^2\cogb^2 \right) + 2\gammab\cogb\left(1-\gammab\cogb\right) + \frac{2}{3}\gammab^3\cogb^3 + \frac{1}{3}\gammab^3\cogb
\end{equation}
of the nonoverlapping case.  
If $\ogb$ is an integer, (\ref{eq:var_reduct_formula}) simplifies to $\frac{2+\gammab^2}{3}$.

@@

\begin{proof} When the sampling problems used in the calculation of $\gbb$ all have optimal solutions that solve (SP), i.e., when $\xs_{j} = \xs$, for all $j=1,2,\ldots, \nbl$, then $\gbb_l = \dbb_l$. 
Therefore, complement of this event provides an upper bound on the probability that $\dbb_l - \gbb_l \neq 0$. 
Let $E^C$ denote the complement of event $E$. 
Using this upper bound and continuing on, we obtain
	\begin{align}
		\p{\dbb_l - \gbb_l \neq 0} & \leq \p{\left( \bigcap_{j=1}^{\nbl} \{\xs_{j} = \xs\} \right)^C} \notag \\
		& = \p{ \bigcup_{j=1}^{\nbl} \{\xs_{j} \neq \xs\}} \notag \\
% 		& \leq \sum_{j=1}^{\nbl} \p{ \xs_j \neq \xs } \notag \\
		& \leq \left( \nbl\right) \p{ \xs_{m_l} \neq \xs }. \notag
	\end{align}
	With a batching structure in which $m_l = \lfloor n_l^{r} \rfloor$ for some $0<r<1$,  $\gamma_l \geq 1$, and by A3, the desired result follows.
\end{proof}

@@

Part (i) of Theorem \ref{thm:strong_consistency} provides conditions under which the point estimator $\gbb$ of OMRP is a consistent estimator of the optimality gap, by establishing almost sure convergence of $\gbb_l - \dbb_l$ to $0$ as $l \rightarrow \infty$. 
Notice that under assumption A1, $\dbb_l \rightarrow \mu_\xh$, a.s. by the strong law of large numbers; as a result, $\gbb \rightarrow \mu_\xh$, a.s. 
Similarly, part (ii) of Theorem \ref{thm:strong_consistency} establishes almost sure convergence of $n_l VG_l - n_l VD_l$ to $0$ as $l \rightarrow \infty$. 
As a result, if $n_l VD_l$ is a consistent estimator of $\sigma^2_{\xh}$, so is $n_l VG_l$.  
Strong consistency of the variance estimator $n_l VD_l$ has been studied in \citep{damerdji1994strong} for the cases of nonoverlapping and maximally overlapping batches.  
Under the additional moment assumption
\begin{description}
	\item[A2$^\prime$]  $\exists \epsilon > 0$ such that $\sup_{\x \in X} \e{f(\x,\xi)^{4+\epsilon}} < \infty$,
\end{description}
for a sampling scheme of $m_l = \lfloor n_l^r \rfloor$, Corollaries 3.4 and 4.2 of \citep{damerdji1994strong} show that $n_l VD_l$ is consistent if $\tfrac{2}{4+\epsilon} < r < 1$ for nonoverlapping batches and $\tfrac{2}{4+\epsilon} < r < \tfrac{1}{2}$ for maximally overlapping batches.

@@

\begin{proof}
	For simplicity of exposition, we drop the subscript $l$ and the $\frac{n_l}{m_l}$ for now and add them in later.  
        Further, we use abbreviations $n_b = \nbl$ to denote the number of batches and $dt = \left(\tfrac{n_l}{m_l} - 1\right) \left(\nbl\right)$ to denote the denominator term in $VG_l$ and $VD_l$. Note that
	\begin{align}
		\e{(nVG - nVD)^2} & = \left( \frac{n}{dt} \right)^2 \e{ \left( \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right] \right)^2 } \notag \\
		& \leq \left( \frac{n}{dt} \right)^2 \e{ n_b \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \label{eq:vvar_conv_pf_1}
	\end{align}
	by the Cauchy-Schwartz inequality, where the second vector in the Cauchy-Schwartz inequality is taken as a vector of ones.  
        By examining the batch structure in Figure \ref{fig:overlap_nonint} and the definition of $\gbb$ in (\ref{eq:gbb}), one can see that the terms of the expectation in (\ref{eq:vvar_conv_pf_1}) are not identically distributed.  
        We will separate these into identically distributed ``center'' batches and ``fringe'' batches.  
        For example, in Figure \ref{fig:overlap_nonint}, only batch 4 is a center batch, while the others are fringe batches.  
        Notice in Figure \ref{fig:overlap_nonint}, we see $\left\lceil \gammab^{-1} \right\rceil = 3$ sets of nonoverlapping batches $\{1,4,7\}$, $\{2,5\}$, and $\{3,6\}$, each of which has two fringe batches.  
        In general, there are $\left\lceil \gammab^{-1} \right\rceil$ sets of nonoverlapping batches, each of which will have two fringe batches, and $n_b - 2\left\lceil \gammab^{-1} \right\rceil$ center batches.

	The fringe batches will come in identically distributed pairs.  
        The first and last batch would be identically distributed, as would the second and second-to-last, etc.  
        We know this because we could reverse the order of the i.i.d.\ sample and perform the batching again to get the exact same batch structure.  
        Rewriting to take this into account, letting $A_j = (\gb_j - \gbb)^2 - (\db_j - \dbb)^2$, and continuing from (\ref{eq:vvar_conv_pf_1}),
	\begin{align*}
		& \left( \frac{n}{dt} \right)^2 n_b \e{ \sum_{1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \\
		 =  & \left( \frac{n}{dt} \right)^2 n_b \e{\left[ \sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
		 + \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
		 + \sum_{j=n_b-\left\lceil \gammab^{-1} \right\rceil+1}^{n_b} \left[ A_j \right]^2 \right]\
		} \\
		 = & \left( \frac{n}{dt} \right)^2 n_b \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } + \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } \\
		 = & \left( \frac{n}{dt} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left[ A_j \right]^2 }
		+ \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 }.
	\end{align*}	
	We have $\left\lceil \gammab^{-1} \right\rceil + 1$ expectation terms, each of which has a coefficient that is less than $\left(\frac{n}{dt}\right)^2n_b^2 < (2m)^2$.  
        So each expectation can be bounded by
	\begin{align}
		\left( 2m \right)^2 \e{ \left[ A_j \right]^2 } & = \left( 2m \right)^2 \e{ \left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^2 \left[(\gb_j - \gbb) + (\db_j - \dbb)\right]^2 } \notag \\
		& \leq \left( 2m \right)^2 \sqrt{\e{\left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^4}} \sqrt{\e{\left[(\gb_j - \gbb) + (\db_j - \dbb)\right]^4 }} \label{eq:var_reduct_cauchy2} \\
		& \leq \left( 2m \right)^2 \sqrt{\e{\left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^4}} \sqrt{8 \left(\e{(\gb_j - \gbb)^4} + \e{(\db_j - \dbb)^4} \right)}, \label{eq:var_reduct_holder2}
	\end{align}
	where equation (\ref{eq:var_reduct_cauchy2}) follows from the Cauchy-Schwartz inequality, and equation (\ref{eq:var_reduct_holder2}) follows from H\"{o}lder's inequality.  
        Since we can bound both expectation terms in (\ref{eq:var_reduct_holder2}) by A2, we can demonstrate $\sqrt{\frac{n}{m}}(nVG - nVD) \xrightarrow{L^2} 0$ by focusing on only one of the terms.  
        Focusing on the first expectation term in (\ref{eq:var_reduct_holder2}) and returning the $\tfrac{n}{m}$, by H\"{o}lder's inequality,
	\begin{align*}
		\frac{n}{m} 4m^2 \e{\left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^4}	& \leq 32 \frac{n}{m} m^2\left( \e{(\db_j - \gb_j)^4} + \e{(\dbb - \gbb)^4} \right).
	\end{align*}	
	By Lemma \ref{lem:gb_gbb_l4}, both expectation terms above converge to zero with exponential rates.  
        With a batching structure $m_l = \lfloor n_l^r \rfloor$ for some $0<r<1$, we see that $\frac{n_l}{m_l} \e{(n_l VG_l - n_l VD_l)^2} \rightarrow 0$.
\end{proof}

@@

\begin{proof} 
%        With $\xh \neq \xs$, 
			Let $X_l = \frac{\dbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, $Y_l = \frac{\gbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, and $Z_l = \frac{\sigma^2_\xh}{\sqrt{n_lVD_l}} \frac{\sqrt{n_lVD_l}}{\sqrt{n_lVG_l}}$. 
			Also let $z_{\alpha}$ denote the $1-\alpha$ quantile of the standard normal distribution. 
        It is suffices to show $Y_lZ_l = \frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, where $\Rightarrow$ denotes convergence in distribution.
			If $\frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, because $t_{d_l,\alpha} \rightarrow z_{\alpha}$ as $l \rightarrow \infty$, we obtain the desired result by rearranging the terms in $\p{\mu_\xh \leq I^G_l}$ and taking the limit as $l \rightarrow \infty$.
        First, we show that $|X_l - Y_l| \rightarrow 0$, a.s.  Note that $|X_l - Y_l| > 0$ if and only if $|\dbb_l - \gbb_l| > 0$.  
        In the proof of Theorem \ref{thm:strong_consistency} we showed that $\left\{ \dbb_l - \gbb_l \neq 0 \right\}$ happens only finitely many times, so $|X_l - Y_l| \rightarrow 0$, a.s.\ by the Borel-Cantelli Lemma. 
        Next, since $X_l \Rightarrow N(0,1)$  by the central limit theorem and $|X_l - Y_l| \rightarrow 0$ in probability, $Y_l \Rightarrow N(0,1)$.  
        By hypothesis and Theorem \ref{thm:strong_consistency}, $Z_l \rightarrow 1$ in probability.  
        Thus, by Slutsky's theorem, $Y_lZ_l \Rightarrow N(0,1)$.
\end{proof}

The asymptotic validity of the OMRP CI requires $n_l VD_l$ to converge in probability to $\sigma^{2}_{\xh}$. 
This can be achieved either by almost sure or mean-square convergence, which gives a larger range of $r$ in the batching structure.
Also, a hypothesis of Theorem~\ref{thm:conf_int} is that $\xh \neq \xs$.  
For $\xh = \xs$, $\mu_\xh = 0$, and therefore, we have $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1$.
